Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-09-25 draftfinalreport_v4.Rnw
minor fix of autoref

The last benefit--cost analysis scenario were performed was one in which more than the minimum proportion of na\"{\i}ve were immunised. In this scenario we did not use the \Sexpr{vacc_reqd_percent}\% of currently na\"{\i}ve population necessary to reach adequate national immunity levels (\autoref{table:coh_vac}), but included additional vaccination so that 50$\%$ of the currently na\"{\i}ve population was immunised, \autoref{table:cost50pc}. In this scenario the additional vaccination reduces the B/C ratio, and the additional vaccines for the extra immunisation mean that the cost per immunised person before the programme becomes costly reduces to \$\Sexpr{break_even_vacc_cost50}  per immunised person \label{table:cost50pc}.

>>>>

The last benefit--cost analysis scenario were performed was one in which more than the minimum proportion of na\"{\i}ve were immunised. In this scenario we did not use the \Sexpr{vacc_reqd_percent}\% of currently na\"{\i}ve population necessary to reach adequate national immunity levels (\autoref{table:coh_vac}), but included additional vaccination so that 50$\%$ of the currently na\"{\i}ve population was immunised, \autoref{table:cost50pc}. In this scenario the additional vaccination reduces the B/C ratio, and the additional vaccines for the extra immunisation mean that the cost per immunised person before the programme becomes costly reduces to \$\Sexpr{break_even_vacc_cost50}  per immunised person \autoref{table:cost50pc}.
